Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-06 Paper.tex
Start smart-contract detailed description

@@

\section{Repositorio}\label{sec:repository}
El código fuente generado en el proyecto está publicado en un repositorio público de GitHub bajo licencia MIT.
\newline\newline
\url{https://github.com/ethereum-internet-access}
\newline
\begin{thebibliography}{9}
\bibitem{spectrumnh}
  \href{https://uk5g.org/media/uploads/resource_files/Spectrum\_NH\_discussion\_paper\_20Feb19.pdf}{5G Spectrum and Neutral Hosting}, Discussion paper, February 2019,
  DCMS Phase 1 5G Testbeds \& Trials Programme
\bibitem{5g} \href{https://en.wikipedia.org/wiki/5G}{https://en.wikipedia.org/wiki/5G}
\bibitem{sdns} Ian F. Akyildiz and Shih-Chun Lin and Pu Wang,
  \textit{Wireless software-defined networks (W-SDNs) and network function virtualization (NFV) for 5G cellular systems:
    An overview and qualitative evaluation}, Computer Networks, 93, 2015
\bibitem{nfv} Jose Ordonez-Lucena et al.
  \textit{Network Slicing for 5G with SDN/NFV: Concepts, Architectures, and Challenges},
   IEEE Communications Magazine ( Volume: 55 , Issue: 5 , May 2017 )
\bibitem{fon} \href{https://es.wikipedia.org/wiki/La_Fonera}{https://es.wikipedia.org/wiki/La\_Fonera}
\bibitem{hotspotme} \href{https://devpost.com/software/hotspot-me}{https://devpost.com/software/hotspot-me}
\bibitem{hostapd} \href{https://w1.fi/hostapd/}{https://w1.fi/hostapd/}
\bibitem{iptables} \href{https://linux.die.net/man/8/iptables}{https://linux.die.net/man/8/iptables}
\bibitem{dnsmasq} \href{https://en.wikipedia.org/wiki/Dnsmasq}{https://en.wikipedia.org/wiki/Dnsmasq}
\bibitem{osmc} \href{https://osmc.tv/}{https://osmc.tv/}
\bibitem{5gcity} \href{https://www.5gcity.eu/}{https://www.5gcity.eu/}
\bibitem{allen}  \href{Christopher Allen, The path to self sovereign identity, 2016}
  {http://www.lifewithalacrity.com/2016/04/the-path-to-self-soverereign-identity.html}
\bibitem{identicat}
  \href{Catalonia to Build DLT-Based Identity, Coindesk, 2019}{https://www.coindesk.com/catalonia-government-to-build-dlt-based-identity-platform-for-citizens}

>>>>

\subsubsection{Smart contract}

The smart contract\cite{state-channel-contract-a} used
to implement the proof of concept consists on a simple
uni-directional micro-payment channel that is Ownable
depending on OpenZeppelin contract; uses also OpenZeppelin's
SafeMath library in order to perform accounting operations
and finally uses also OpenZeppelin's ECDSA library to support
the signature validation on the closing channel operation.

Main data stucture of the contract described below:

\paragraph{ChannelData} Includes payer ethereum address,
its state channel ephemeral address, deposit amount, opening time
and a boolean representing the open/close status of the channel.

Contract's storage variables:

\paragraph{channelCount} uint256 variable that increments
in a unit every time a user opens a channel. This operation
does not rely on SafeMath since it's virtually impossible to
overflow a uint256 storage record.

\paragraph{channelMapping} Holding a key-value map between
channelCount values and channelData structures.

\paragraph{pricePerSecond} Constant keeping track of
service price per second.

The main methods of the smart contract:

\paragraph{openChannel} receives as parameters, the ephemeral address
of the user and also the purchased service value.

\paragraph{closeChannel}

@@

\section{Repositorio}\label{sec:repository}
El código fuente generado en el proyecto está publicado en un repositorio público de GitHub bajo licencia MIT.
\newline\newline
\url{https://github.com/ethereum-internet-access}
\newline
\begin{thebibliography}{9}
\bibitem{spectrumnh}
  \href{https://uk5g.org/media/uploads/resource_files/Spectrum\_NH\_discussion\_paper\_20Feb19.pdf}{5G Spectrum and Neutral Hosting}, Discussion paper, February 2019,
  DCMS Phase 1 5G Testbeds \& Trials Programme
\bibitem{5g} \href{https://en.wikipedia.org/wiki/5G}{https://en.wikipedia.org/wiki/5G}
\bibitem{sdns} Ian F. Akyildiz and Shih-Chun Lin and Pu Wang,
  \textit{Wireless software-defined networks (W-SDNs) and network function virtualization (NFV) for 5G cellular systems:
    An overview and qualitative evaluation}, Computer Networks, 93, 2015
\bibitem{nfv} Jose Ordonez-Lucena et al.
  \textit{Network Slicing for 5G with SDN/NFV: Concepts, Architectures, and Challenges},
   IEEE Communications Magazine ( Volume: 55 , Issue: 5 , May 2017 )
\bibitem{fon} \href{https://es.wikipedia.org/wiki/La_Fonera}{https://es.wikipedia.org/wiki/La\_Fonera}
\bibitem{hotspotme} \href{https://devpost.com/software/hotspot-me}{https://devpost.com/software/hotspot-me}
\bibitem{hostapd} \href{https://w1.fi/hostapd/}{https://w1.fi/hostapd/}
\bibitem{iptables} \href{https://linux.die.net/man/8/iptables}{https://linux.die.net/man/8/iptables}
\bibitem{dnsmasq} \href{https://en.wikipedia.org/wiki/Dnsmasq}{https://en.wikipedia.org/wiki/Dnsmasq}
\bibitem{osmc} \href{https://osmc.tv/}{https://osmc.tv/}

\bibitem{state-channel-contract-a}
  \href{state-channel-contract-a on GitHub}{https://github.com/ethereum-internet-access/state-channel-contract-a}
\bibitem{etherwall}
  \href{etherwall on GitHub}{https://github.com/ethereum-internet-access/etherwall}
\bibitem{etherdoor}
  \href{etherdoor on GitHub}{https://github.com/ethereum-internet-access/etherdoor}

\bibitem{5gcity} \href{https://www.5gcity.eu/}{https://www.5gcity.eu/}
\bibitem{allen}  \href{Christopher Allen, The path to self sovereign identity, 2016}
  {http://www.lifewithalacrity.com/2016/04/the-path-to-self-soverereign-identity.html}
\bibitem{identicat}
  \href{Catalonia to Build DLT-Based Identity, Coindesk, 2019}{https://www.coindesk.com/catalonia-government-to-build-dlt-based-identity-platform-for-citizens}
